\documentclass[12pt,twoside]{article}
\usepackage{amssymb, amsmath, mathrsfs, epsfig}
\usepackage{fancyhdr}
\usepackage{tikz}
\setlength{\voffset}{-1in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{6.5in}
\setlength{\hoffset}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\marginparsep}{0in}
\setlength{\marginparwidth}{0in}
\setlength{\headsep}{0.25in}
\setlength{\headheight}{0.5in}
\pagestyle{fancy}

\fancyhead[LO,LE]{Math 106L}
\fancyhead[RO,RE]{Lab answer}
\chead{\textbf{Newton's Law of Motion}}
\cfoot{}
\fancyfoot[LO,LE]{}
\fancyfoot[RO,RE]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\footrulewidth}{0.5pt}
\parindent 0in

\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Sp}{\vspace{.5in}}
\newcommand{\defn}{\paragraph*{Definition}}
\newcommand{\example}{\paragraph*{Example}}
\newcommand{\examples}{\paragraph*{Examples}}
\newcommand{\qns}{\paragraph*{Questions}}
\newcommand{\qn}{\paragraph*{Question}}
\newcommand{\blank}[1]{\underline{\hspace{#1}}}
\newcommand{\dsst}{\displaystyle}

\begin{document}
11. A particle moves on a line with acceleration $s''(t) = -4t$. Suppose that $s(0) = 6$ and $s'(0) = 24$. Find the functions $s(t)$ and $s'(t)$. Graph the functions $s(t)$, $s'(t)$ and $s''(t)$ on the same set of axes and describe the motion in words.

The initial value problem is given by 

\begin{align*}
s''(t) &= -4t \\
s'(0) &= 24 \\
s(0) & = 6
\end{align*}

The solution to the i.v.p. is $s(t) = -\frac{2}{3} t^3 + 24t + 6$. We also know that $s'(t) = -2t^2 + 24$. 

Describe motion of this man.
\begin{itemize}
\item At time 0 seconds, the particle is 6 units to the right of the reference point. It is moving to the right at a speed of 24. 
\item The velocity decreases throughout the entire motion, since the acceleration is negative.  
\item The particle moves to the right with decreasing speed for $2\sqrt{3}$ units of time.
\item At time $t = 2\sqrt{3}$, the particle comes to an instant stop at $32\sqrt{3} + 6$. 
\item Following that, the particle moves to left with an increasing speed. 
\item The particle passes the reference point at $t = 6.1213$
\end{itemize}

\end{document}
